\chapter{Introduction}
\label{chap:intro}

This chapter gives a introduction of the project including products, document structure, process control, etc.

\section{Document tree}

Below is an overview of the document tree that is used in the project:
\begin{listb}
# Product backlog and road map (company wide).
# Requirement document for each product.
	## Standing from the user point of view
	## Describe features, use cases, performance, etc. 
# Algorithm document.
	## Intelligence to realize the requirement abstractly.
	## Data needed should be described here.
# Design document (can be in multiple level).
    ## describe subsystems, interfaces, data flow, technology, diagnostic, etc.
	## Balance flexibility/cost/time/robust/etc
	## Balance between complexity/flexibility 
# Code comment. 
    ## Describe the detailed and low-level design of class, function, variable, etc.
    ## Is also one kind of design document.
# Test document.
    ## Describe test plan and test case to test software functionality and to verify requirements. 
    ## Include unit test to test software functionality
    ## Include progression and regression tests to verify requirements are met. 
# Development process document for progress tracking/communication/etc.
	## Methodologies: scrum, water fall, etc
	## Tools such as PERT/excel/etc are useful
\end{listb}

\section{Products}


\begin{listb}
\ListProperties(CtrCom1=\counter{\textbf{Product}})
%\ListProperties(Style1=\bfseries)
# Command line interactive trading system 
  ##	Allow user to view/create/cancel orders using command line
  ##	Manage activity history
# Offline stock screener (with three sub-products)
  ## Screening using historical quotes
     ### Break over resist
     ### Bounce from support
     ### Trend       
  ## Screening using historical financial
     ### Value 
     ### Financial strength
     ### Grow 
     ### Sentiment  
  ## Screening using events/news/economic indicators 
     ### Predict trend based on financial indicators/event 
# Automated online stock monitor
  ## Submit/cancel order based on real time quote info
     ### Only sell a stock only if the price falls below stop price longer than a specified time
# Automated online stock screener
  ## Screening stock using real time quotes
# Trading simulator, allows user to test their strategies
\end{listb}
