\chapter{Working plan}
\label{chap:plan}

This chapter describes the guidelines and way of working in the project, including:
\begin{listb}
\ListProperties(CtrCom1=\counter{})
%\ListProperties(Style1=\bfseries)
# Plan to implement software. 
  ## Scrumb? 
# Plan to learn new skills.
  ## This should be put into the daily/weekly/monthly plan.
# Daily, weekly and monthly planning. 
  ## Every week there should be a goal. 
  ## Every week there should be some time for learning new skills.
  ## Every month/weeks, there should be a milestone.
  ## Every week should summarize what has learned and what to improve.    
\end{listb}

\section{Todo List}

\begin{listb}
# Stock Server - search algorithm
  ## add bunch of technical indicators
# Stock Server - data update
  ## Convert stock server into a conscole app.
  ## Add functionality to handle the case when Reuters or Yahoo makes some change. 
  ## Synchronize database update by stock server and web request
# Web application
  ## Multi-langurage support
  ## User Authentication
  ## User account mangement
  ## Payment system
  ## SSL
  ## UI, Chart
\end{listb} 


\section{Issue List}

\begin{listb}
# Some stocks, industries and sectors do not have name.
# Web crawler is not robust to website change.
\end{listb} 



\newpage
\section*{Week01}

\begin{table}
\begin{tabular}{p{3cm}|p{8cm}} \hline
Goal & 
\begin{listb}
# Get IB paper trading account.
# Summit/manage orders using IB CSharp API.
# Capture quotes from screen or get them from API. 
\end{listb} \\ \hline
Achievements &
\begin{listb}
# Parsing HTML using Agility pack
# Parallel execution of Actions
\end{listb} \\ \hline
Learning points &
\begin{listb}
# Reflection
# Recursive programming
\end{listb} \\ \hline

\end{tabular}
\end{table}
